---
title: "Exe"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
description: >
  `Exe` examples.
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Exe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette provides examples for the [Exe()] function in the `yacR` package.

```{r, warning = FALSE, results = 'hide', message = FALSE}
library(Ryacas)
library(yacR)
```

We start with the matrix $\mathbf{A}$ whose elements are
$\left\{ a, b, c, d \right\}$.


```{r}
A <- matrix(c("a", "b", "c", "d"), ncol = 2, byrow = TRUE)
```

```{r, echo=FALSE, results = "asis"}
cat(
  "\\begin{align*}",
  "\\mathbf{A} &=",
  as.tex(A),
  "\\end{align*}",
  sep = ""
)
```

We need to convert the matrix `A` into a `yac_symbol` first.
This can be done using the `Ryacas` function `ysym()`.

```{r}
A <- ysym(A)
```

## Example 1

The `Determinant` of `A` can be obtained in `Yacas`
with the expression `Determinant(A)`.

```{r}
expr1 <- paste0("Determinant(", A, ")")
```

The following returns a **`yac_symbol`** output.

```{r}
yac_symbol <- Exe(expr1)
str(yac_symbol)
```

The following returns a **string** output.

```{r}
string <- Exe(expr1, format = "str")
str(string)
```

The following returns a **`LaTeX` mathematics** output.

```{r}
latex <- Exe(expr1, format = "tex")
str(latex)
```

LaTeX mathematics can be displayed **inline**
by enclosing the code or object with ``$`r `$``.

$`r latex`$

It can be displayed as a **centered equation**
by enclosing the code or object with ``$$`r `$$``.

$$`r latex`$$

It can also be displayed as an `R` code chuck.
Remember to set `results = "asis"`.

```{r, results = "asis"}
cat(
  "\\begin{align*}",
  "\\det \\mathbf{A} &=",
  latex,
  "\\end{align*}",
  sep = ""
)
```

The following returns an **`R` `expression`** output.

```{r}
yacR::Exe(expr1, R = TRUE)
```

## Example 2

In the following example we derive the `Transpose` of the matrix `A`
with the expression `Transpose(A)`.

```{r}
expr2 <- paste0("Transpose(", A, ")")
```

The following returns a **`yac_symbol`** output.

```{r}
yac_symbol <- Exe(expr2)
str(yac_symbol)
```

The following returns a **string** output.

```{r}
string <- Exe(expr2, format = "str")
str(string)
```

The following returns a **`LaTeX` mathematics** output.

```{r}
latex <- Exe(expr2, format = "tex")
str(latex)
```

```{r, results = "asis"}
cat(
  "\\begin{align*}",
  "\\mathbf{A}^{\\mathsf{T}} &=",
  latex,
  "\\end{align*}",
  sep = ""
)
```

The following returns an **`R` `expression`** output.

```{r}
yacR::Exe(expr2, R = TRUE)
```

## Numeric

The `R` expression outputs can be evaluated numerically using the `eval` function.
The symbols `a`, `b`, `c`, and `d`
should have values in the environment `eval` is using.

```{r}
a <- 1
b <- 2
c <- 3
d <- 4
```

Below is the numerical result for example 1
```{r}
eval(yacR::Exe(expr1, R = TRUE))
```

which is equal to the following.

```{r}
det(matrix(1:4, ncol = 2, byrow = TRUE))
```

Below is the numerical result for example 2

```{r}
eval(yacR::Exe(expr2, R = TRUE))
```

which is equal to the following.

```{r}
t(matrix(1:4, ncol = 2, byrow = TRUE))
```
